### 2019-04-09 2_metg.tex
Edits from Alex.

In Figure~\ref{fig:efficiency-mpi}, we see that
efficiency starts at 100\%. Initially task granularity
shrinks with minimal change in efficiency. However as task
granularity shrinks further, efficiency drops more rapidly, leading
to an asymptote as overhead dominates useful work.

>>>>

In Figure~\ref{fig:efficiency-mpi},
efficiency starts at 100\%. Initially task granularity
shrinks with minimal change in efficiency. However as task
granularity shrinks further, efficiency drops more rapidly, leading
to an asymptote as runtime overhead dominates useful work.

### 2019-04-09 5_evaluation.tex
Edits from Alex.

The least complicated pattern (stencil) is most favorable
to MPI, as it represents a truly bulk synchronous task graph with no
opportunity for task parallelism. For the stencil pattern, the
dominating factor is the basic overhead of executing a task, which is
minimal for MPI as the Task Bench implementation is bulk synchronous
and simply executes tasks one after another in alternation with
communication phases. In contrast, the asynchronous execution
mechanisms of the other systems are pure overhead in this scenario.

@@

The MPI implementation of Task Bench, being bulk synchronous,
suffers the most under load imbalance. The biggest
difference is at large task granularities, where the imbalance has the
effect of putting an upper bound on MPI efficiency. At smaller task
granularities the effect shrinks and may even reverse as systems hit
their fundamental limits due to overhead.

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs only partially mitigates the
load imbalance between tasks. Systems that provide an
additional on-node work stealing capability (such as Chapel with the distrib scheduler) see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. For example, Chapel's default (non-work-stealing) scheduler outperforms Chapel distrib at very small task granularities.

>>>>

The least complicated pattern (stencil) is most favorable
to MPI, as it provides no
opportunity for task parallelism. For the stencil pattern, the
dominating factor is the basic overhead of executing a task, which is
minimal for MPI as the Task Bench implementation simply executes tasks one after another in alternation with
communication phases. In contrast, the asynchronous execution
mechanisms of other systems are pure overhead in this scenario.

@@

The MPI implementation of Task Bench, with its distinct computation and communication phases,
suffers the most under load imbalance. The biggest
difference is at large task granularities, where the imbalance has the
effect of putting an upper bound on MPI efficiency. At smaller task
granularities the effect shrinks and may even reverse as systems hit
their fundamental limits due to overhead.

The difference between the remaining systems is due primarily to
different scheduling behaviors. The execution of 4
simultaneous task graphs only partially mitigates the
load imbalance between tasks. Systems that provide an
additional on-node work stealing capability (such as Chapel with the distrib scheduler) see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. For example, Chapel's default (non-work-stealing) scheduler outperforms Chapel distrib at very small task granularities.

### 2019-04-09 6_related.tex
Edits from Alex.

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest study we're aware of,
for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI). Other
studies usually lack a comprehensive evaluation, even if multiple
implementations are available.

>>>>

Though smaller than full applications, mini-apps can be challenging to
implement to a level of quality sufficient for conducting comparative
studies between programming systems. The largest study we know of,
for the mini-app LULESH~\cite{LULESH13}, compares 7 programming
systems (Chapel, Charm++, CUDA, Lizst, Loci, OpenMP, and MPI). Other
studies usually lack a comprehensive evaluation, even if multiple
implementations are available:
